---
title: "Library Occupancy Over Time"
output:
  html_document:
    highlight: "default"
    theme: "simplex"
    toc: true
---

```{r echo=FALSE}
hunt_data <- read.csv("hunt.csv")

hill_data <- read.csv("hill.csv")

to_datetime <- function(datetime_string) {
  return(as.POSIXct(datetime_string, tz = "", format = "%Y-%m-%d %H:%M:%OS"))
}

n_hours_ago <- function(current_datetime, hours) {
  return()
}

entries_since_n_hrs_ago <- function(entries, datetimes, hours) {
  most_recent_datetime <- tail(datetimes, n = 1)
  n_hrs_ago <- most_recent_datetime - 60 * 60 * hours
  entries_since <- subset(entries, datetimes >= n_hrs_ago)
  return(entries_since)
}
```

# Hill

## Stats

### Current

```{r echo=FALSE}
most_recent_entry <- tail(hill_data, n = 1)
```

As of `r most_recent_entry$datetime` there are `r most_recent_entry$total.count` people in Hill (`r most_recent_entry$total.percent * 100`% capacity)

East: `r most_recent_entry$east.count` (`r most_recent_entry$east.percent * 100`% capacity)

Tower: `r most_recent_entry$tower.count` (`r most_recent_entry$tower.percent * 100`% capacity)

West: `r most_recent_entry$west.count` (`r most_recent_entry$west.percent * 100`% capacity)


### Recent
```{r echo=FALSE}
hill_datetimes <- to_datetime(hill_data$datetime)

past_week_entries <-
  entries_since_n_hrs_ago(hill_data, hill_datetimes, 24 * 7)

past_day_entries <-
  entries_since_n_hrs_ago(hill_data, hill_datetimes, 24)

past_three_hrs_entries <-
  entries_since_n_hrs_ago(hill_data, hill_datetimes, 3)
```

| Since           | Average Total Count                         | Average Overall Percent                             |
| --------------- | ------------------------------------------- | --------------------------------------------------- |
| Three hours ago | `r mean(past_three_hrs_entries$total.count)`| `r mean(past_three_hrs_entries$total.percent) * 100`|
| One day ago     | `r mean(past_day_entries$total.count)`      | `r mean(past_day_entries$total.percent) * 100`      |
| One week ago    | `r mean(past_week_entries$total.count)`     | `r mean(past_week_entries$total.percent) * 100`     |

## Counts

```{r echo=FALSE}
entry_datetimes <- to_datetime(hill_data$datetime)

# allow legend to be out of the graph area
par(xpd = TRUE)

plot(
  entry_datetimes, hill_data$east.count,
  col = "red", ylim = c(0, 1100),
  xlab = "Datetime", ylab = "Count"
)
lines(entry_datetimes, hill_data$east.count, col = "red")

points(entry_datetimes, hill_data$tower.count, col = "green")
lines(entry_datetimes, hill_data$tower.count, col = "green")

points(entry_datetimes, hill_data$west.count, col = "blue")
lines(entry_datetimes, hill_data$west.count, col = "blue")

points(entry_datetimes, hill_data$total.count)
lines(entry_datetimes, hill_data$total.count)

legend(
  "topleft",
  inset = c(0, -0.25), legend = c("Total", "East", "Tower", "West"),
  fill = c("black", "red", "green", "blue")
)
```

## Percents

```{r echo=FALSE}
entry_datetimes <- to_datetime(hill_data$datetime)

# allow legend to be out of the graph area
par(xpd = TRUE)


plot(
  entry_datetimes, hill_data$east.percent,
  col = "red", ylim = c(0, 1),
  xlab = "Datetime", ylab = "Current / Capacity"
)
lines(entry_datetimes, hill_data$east.percent, col = "red")

points(entry_datetimes, hill_data$tower.percent, col = "green")
lines(entry_datetimes, hill_data$tower.percent, col = "green")

points(entry_datetimes, hill_data$west.percent, col = "blue")
lines(entry_datetimes, hill_data$west.percent, col = "blue")

points(entry_datetimes, hill_data$total.percent, col = "black")
lines(entry_datetimes, hill_data$total.percent, col = "black")

legend(
  "topleft",
  inset = c(0, -0.25), legend = c("Total", "East", "Tower", "West"),
  fill = c("black", "red", "green", "blue")
)
```

---

# Hunt

## Stats

### Current

```{r echo=FALSE}
most_recent_entry <- tail(hunt_data, n = 1)
```

As of `r most_recent_entry$datetime` there are `r most_recent_entry$total.count` people in Hunt (`r most_recent_entry$total.percent * 100`% capacity)

Level 2: `r most_recent_entry$level2.count` (`r most_recent_entry$level2.percent * 100`% capacity)

Level 3: `r most_recent_entry$level3.count` (`r most_recent_entry$level3.percent * 100`% capacity)

Level 4: `r most_recent_entry$level4.count` (`r most_recent_entry$level4.percent * 100`% capacity)

Level 5: `r most_recent_entry$level5.count` (`r most_recent_entry$level5.percent * 100`% capacity)

### Recent

```{r echo=FALSE}
hunt_datetimes <- to_datetime(hunt_data$datetime)

past_week_entries <-
  entries_since_n_hrs_ago(hunt_data, hunt_datetimes, 24 * 7)

past_day_entries <-
  entries_since_n_hrs_ago(hunt_data, hunt_datetimes, 24)

past_three_hrs_entries <-
  entries_since_n_hrs_ago(hunt_data, hunt_datetimes, 3)
```

| Since           | Average Total Count                         | Average Overall Percent                             |
| --------------- | ------------------------------------------- | --------------------------------------------------- |
| Three hours ago | `r mean(past_three_hrs_entries$total.count)`| `r mean(past_three_hrs_entries$total.percent) * 100`|
| One day ago     | `r mean(past_day_entries$total.count)`      | `r mean(past_day_entries$total.percent) * 100`      |
| One week ago    | `r mean(past_week_entries$total.count)`     | `r mean(past_week_entries$total.percent) * 100`     |

## Counts

```{r echo=FALSE}
entry_datetimes <- to_datetime(hunt_data$datetime)

# allow legend to be out of the graph area
par(xpd = TRUE)


plot(
  entry_datetimes, hunt_data$level2.count,
  col = "green", ylim = c(0, 600),
  xlab = "Datetime", ylab = "Count"
)
lines(entry_datetimes, hunt_data$level2.count, col = "green")

points(entry_datetimes, hunt_data$level3.count, col = "red")
lines(entry_datetimes, hunt_data$level3.count, col = "red")

points(entry_datetimes, hunt_data$level4.count, col = "blue")
lines(entry_datetimes, hunt_data$level4.count, col = "blue")

points(entry_datetimes, hunt_data$level5.count, col = "orange")
lines(entry_datetimes, hunt_data$level5.count, col = "orange")

points(entry_datetimes, hunt_data$total.count, col = "black")
lines(entry_datetimes, hunt_data$total.count, col = "black")


legend(
  "topleft",
  inset = c(0, -0.25),
  legend = c("Total", "Level 2", "Level 3", "Level 4", "Level 5"),
  fill = c("black", "green", "red", "blue", "orange")
)
```

## Percents

```{r echo=FALSE}
entry_datetimes <- to_datetime(hunt_data$datetime)

# allow legend to be out of the graph area
par(xpd = TRUE)

plot(entry_datetimes, hunt_data$level2.percent,
  col = "green", ylim = c(0, 1),
  xlab = "Datetime", ylab = "Current / Capacity"
)
lines(entry_datetimes, hunt_data$level2.percent, col = "green")

points(entry_datetimes, hunt_data$level3.percent, col = "red")
lines(entry_datetimes, hunt_data$level3.percent, col = "red")

points(entry_datetimes, hunt_data$level4.percent, col = "blue")
lines(entry_datetimes, hunt_data$level4.percent, col = "blue")

points(entry_datetimes, hunt_data$level5.percent, col = "orange")
lines(entry_datetimes, hunt_data$level5.percent, col = "orange")

points(entry_datetimes, hunt_data$total.percent, col = "black")
lines(entry_datetimes, hunt_data$total.percent, col = "black")

legend(
  "topleft",
  inset = c(0, -0.25),
  legend = c("Total", "Level 2", "Level 3", "Level 4", "Level 5"),
  fill = c("black", "green", "red", "blue", "orange")
)
```

---

# Hill vs Hunt

## Counts

```{r echo=FALSE}
# allow legend to be out of the graph area
par(xpd = TRUE)

plot(
  to_datetime(hill_data$datetime), hill_data$total.count,
  type = "p", col = "blue", ylim = c(0, 1000),
  xlab = "Datetime", ylab = "Count"
)
lines(
  to_datetime(hill_data$datetime), hill_data$total.count,
  col = "blue"
)

points(
  to_datetime(hunt_data$datetime), hunt_data$total.count,
  col = "red"
)
lines(
  to_datetime(hunt_data$datetime), hunt_data$total.count,
  col = "red"
)

legend(
  "topleft",
  inset = c(0, -0.25),
  legend = c("Hill", "Hunt"),
  fill = c("blue", "red")
)
```

## Percents

```{r echo=FALSE}
# allow legend to be out of the graph area
par(xpd = TRUE)

plot(
  to_datetime(hill_data$datetime), hill_data$total.percent,
  type = "p", col = "blue", ylim = c(0, 1),
  xlab = "Datetime", ylab = "Current / Capacity"
)
lines(
  to_datetime(hill_data$datetime), hill_data$total.percent,
  col = "blue"
)

points(
  to_datetime(hunt_data$datetime), hunt_data$total.percent,
  col = "red"
)
lines(
  to_datetime(hunt_data$datetime), hunt_data$total.percent,
  col = "red"
)

legend(
  "topleft",
  inset = c(0, -0.25),
  legend = c("Hill", "Hunt"),
  fill = c("blue", "red")
)
```
