---
title: "Library Busyness Over Time"
output:
  html_document:
    highlight: "default"
    theme: "simplex"
    toc: true
params:
  hill_data: NULL
  hunt_data: NULL
---

```{r echo=FALSE}
library(ggplot2)
library(tidyr)

to_datetime <- function(datetime_string) {
  return(as.POSIXct(datetime_string, tz = "", format = "%Y-%m-%d %H:%M:%OS"))
}

entries_since_n_hrs_ago <- function(entries, datetimes, hours) {
  most_recent_datetime <- tail(datetimes, n = 1)
  n_hrs_ago <- most_recent_datetime - 60 * 60 * hours
  entries_since <- subset(entries, datetimes >= n_hrs_ago)
  return(entries_since)
}
```

# Hill

```{r echo=FALSE}
hill_datetimes <- to_datetime(hill_data$record_datetime)

hill_counts_long <- data.frame(
  record_datetime = hill_datetimes,
  east = hill_data$east_count,
  tower = hill_data$tower_count,
  west = hill_data$west_count
) %>%
  pivot_longer(c(east, tower, west), names_to = "zone", values_to = "people")

hill_percents <- data.frame(
  record_datetime = hill_datetimes,
  total = hill_data$total_percent
)

most_recent_entry <- tail(hill_data, n = 1)
```

## Stats

### Current

#### As of `r most_recent_entry$record_datetime` there are `r most_recent_entry$total_count` people in Hill (`r most_recent_entry$total_percent * 100`% capacity)

East: `r most_recent_entry$east_count` (`r most_recent_entry$east_percent * 100`% capacity)

Tower: `r most_recent_entry$tower_count` (`r most_recent_entry$tower_percent * 100`% capacity)

West: `r most_recent_entry$west_count` (`r most_recent_entry$west_percent * 100`% capacity)


### Recent
```{r echo=FALSE}
past_week_entries <-
  entries_since_n_hrs_ago(hill_data, hill_datetimes, 24 * 7)

past_day_entries <-
  entries_since_n_hrs_ago(hill_data, hill_datetimes, 24)

past_three_hrs_entries <-
  entries_since_n_hrs_ago(hill_data, hill_datetimes, 3)
```

| Since           | Average Total Count                         | Average Overall Percent                             |
| --------------- | ------------------------------------------- | --------------------------------------------------- |
| Three hours ago | `r mean(past_three_hrs_entries$total_count)`| `r mean(past_three_hrs_entries$total_percent) * 100`|
| One day ago     | `r mean(past_day_entries$total_count)`      | `r mean(past_day_entries$total_percent) * 100`      |
| One week ago    | `r mean(past_week_entries$total_count)`     | `r mean(past_week_entries$total_percent) * 100`     |

## Counts

```{r echo=FALSE, fig.width=10, fig.height=6}
ggplot(hill_counts_long, aes(x = record_datetime, y = people, fill = zone)) +
  geom_area(alpha = 0.5, colour = "black", linewidth = 0.2) +
  xlab("Datetime") +
  ylab("# of people")
```

## Percents

```{r echo=FALSE, fig.width=10, fig.height=6}
ggplot(hill_percents, aes(x = record_datetime, y = total)) +
  geom_area(colour = "black", linewidth = 0.5, fill = "blue", alpha = 0.3) +
  xlab("Datetime") +
  ylab("% capacity") +
  ylim(0, 1)
```

---

# Hunt

```{r echo=FALSE}
hunt_datetimes <- to_datetime(hunt_data$record_datetime)

hunt_counts_long <- data.frame(
  record_datetime = hunt_datetimes,
  level2 = hunt_data$level2_count,
  level3 = hunt_data$level3_count,
  level4 = hunt_data$level4_count,
  level5 = hunt_data$level5_count
) %>%
  pivot_longer(
    c(level2, level3, level4, level5),
    names_to = "zone", values_to = "people"
  )

hunt_percents <- data.frame(
  record_datetime = hunt_datetimes,
  total = hunt_data$total_percent
)

most_recent_entry <- tail(hunt_data, n = 1)
```

## Stats

### Current

#### As of `r most_recent_entry$record_datetime` there are `r most_recent_entry$total_count` people in Hunt (`r most_recent_entry$total_percent * 100`% capacity)

Level 2: `r most_recent_entry$level2_count` (`r most_recent_entry$level2_percent * 100`% capacity)

Level 3: `r most_recent_entry$level3_count` (`r most_recent_entry$level3_percent * 100`% capacity)

Level 4: `r most_recent_entry$level4_count` (`r most_recent_entry$level4_percent * 100`% capacity)

Level 5: `r most_recent_entry$level5_count` (`r most_recent_entry$level5_percent * 100`% capacity)

### Recent

```{r echo=FALSE}
past_week_entries <-
  entries_since_n_hrs_ago(hunt_data, hunt_datetimes, 24 * 7)

past_day_entries <-
  entries_since_n_hrs_ago(hunt_data, hunt_datetimes, 24)

past_three_hrs_entries <-
  entries_since_n_hrs_ago(hunt_data, hunt_datetimes, 3)
```

| Since           | Average Total Count                         | Average Overall Percent                             |
| --------------- | ------------------------------------------- | --------------------------------------------------- |
| Three hours ago | `r mean(past_three_hrs_entries$total_count)`| `r mean(past_three_hrs_entries$total_percent) * 100`|
| One day ago     | `r mean(past_day_entries$total_count)`      | `r mean(past_day_entries$total_percent) * 100`      |
| One week ago    | `r mean(past_week_entries$total_count)`     | `r mean(past_week_entries$total_percent) * 100`     |

## Counts

```{r echo=FALSE, fig.width=10, fig.height=6}
ggplot(hunt_counts_long, aes(x = record_datetime, y = people, fill = zone)) +
  geom_area(alpha = 0.5, colour = "black", linewidth = 0.2) +
  xlab("Datetime") +
  ylab("# of people")
```

## Percents

```{r echo=FALSE, fig.width=10, fig.height=6}
ggplot(hunt_percents, aes(x = record_datetime, y = total)) +
  geom_area(colour = "black", linewidth = 0.5, fill = "blue", alpha = 0.3) +
  xlab("Datetime") +
  ylab("% capacity") +
  ylim(0, 1)
```

---

# Hill vs Hunt

```{r echo=FALSE}
combined_data <- data.frame(
  record_datetime = c(hill_datetimes, hunt_datetimes),
  library = c(
    rep("hill", length(hill_datetimes)),
    rep("hunt", length(hunt_datetimes))
  ),
  total_count = c(hill_data$total_count, hunt_data$total_count),
  total_percent = c(hill_data$total_percent, hunt_data$total_percent)
)
```

## Counts

```{r echo=FALSE, fig.width=10, fig.height=6}
ggplot(
  combined_data,
  aes(x = record_datetime, y = total_count, colour = library)
) +
  geom_line(linewidth = 1) +
  xlab("Datetime") +
  ylab("# of people")
```

## Percents

```{r echo=FALSE, fig.width=10, fig.height=6}
ggplot(
  combined_data,
  aes(x = record_datetime, y = total_percent, colour = library)
) +
  geom_line(linewidth = 1) +
  xlab("Datetime") +
  ylab("% capacity")
```
